\chapter{Team assignments}

In this chapter, we are describing motivation, development, support and usage of team assignments. This functionality was developped in summer of 2015 and then used and tested on Modern Approaches to Webdesign course during winter semester of 2016 at our faculty. Since then, multiple courses used team assignment functionality in Courses 2 Learning management system.

\section{Motivation}

Computer Science students are often taught many different types of algorithms, matematics and programmings languages. This is very beneficial to them since many hard skills will be reqired in their future career. But on the other side of this, these students are lackings skills in teamwork, constructive critisism, the ability of self\-reflection or job evaluation.  These skills are essential in ther future jobs or science career however none or very little effort is put to teach students these skills. 


This is why, throughout this work, we are introducing new concepts of assignments for students. These concepts are focused to teach students how to work in teams, teach them constructive critisism or self\-reflection. In this chapter, we describe implementing and usage of one of these concepts, team assignments. With this term, we mean an assignment, which students solve in small teams, which is beneficial for them in multiple ways. This way, student can pick any part of the project he wants to solve. What is more, we reqire peer and team reviews, which can give him feedback on how well he did it. 

This work is also a subject of many other researchers at our faculty such as Veronika Dropcova's research \cite{dropcova}, which is focusing on how students interact with each other and solve this assignments. In this work we focus mostly on implementation and support for this research.


\section{Semantics}
Now, let's describe in detail, how we implemented team assignments in Courses 2 learning management system.

\subsection{Team forming}

\subsection{Assignment submission}

\subsection{Peer review}

\subsection{Teamwork review}

\section{Implementation}
odofjasdofij