\chapter*{Conclusion}
\addcontentsline{toc}{chapter}{Conclusion}

\section*{Summary}
\markright{CONCLUSION}

The main goal of this thesis was to design and develop Courses 2 Assignments module. Courses 2 is a modular Learning Management System created in 2014 by Jakub Culik \cite{culik}. This system was build on modified CodeIgniter, modern PHP programming language framework with MVC architecture pattern with added support for HMVC architecture. We analysed the former Assignments module of this system and iteratively improved its structure, functionality and behaviour.

We introduced Team Projects including team work support and mutual peer feedback within teams, which aims to teach teamwork and soft skills to the students. We also introduced peer review feedback and incorporating of this feedback into a new submission, called an improved submission, which is a concept that aims to teach constructive criticism of other student's work and incorporation of this criticism into student's own work. Third important improvement is Assignment Mirroring. With Assignment Mirroring, every assignment students submits by an URL is mirrored on our servers. Our mirroring algorithm offers some superior functionalities, such as automatic log in of a user, mirroring of HTTP status codes, crawling of HTML and CSS files and serving of these documents on our servers. As a result, our mirrored web pages behave exactly as the original web pages, except for dynamic content. These assignments are mostly web pages created for Web Technology and Methodology course.

With analysis of student's feedback we also proposed new usability improvements. Most significant of them is Assignments Dashboard, which reminds students important dates, evaluations and feedbacks.

This work is also closely linked to other PhD. student's work, such as Veronika Drop\v{c}ov\'{a}'s research \cite{dropcova}.

\section*{Results}
Our work resulted in better Assignments module with improved usability and new learning concepts implemented. Team projects, Improved Submissions, Assignment Dashboard are already used in the learning process at our faculty in courses like Web Design Technology and Methodology or Algorithms and Data Structures.

Other concepts like Assignments Mirroring are implemented and ready for production with the expectancy to be used in the next winter semester.

Usability improvements we proposed and designed also led to better student satisfaction rate with the system and decreased student's frequently asked questions.

\section*{Future work}
This  work included a wide range of analytics and improvements, however, we believe there are still plenty more features to be added to the Courses 2 assignments module. This includes mostly new usability improvements, refactoring, evaluation of assignments and other nice-to-have features.

One of the desired improvements is automated evaluation of student's work. This may be done mainly with Assignments Mirroring. While we are mirroring these web pages, we may automatically evaluate for example validity of their HTML and CSS source code.

Another useful improvement is redesigning of user interface of the whole module. This module was created by multiple students and there is still a room to improve.
